Flatiron cleaning

### 2021-11-02 Rmd/rdi analysis.Rmd
Fix levels, models, therapy groups, etc

  # 3. Combined Multiple Administrations----
  # combined multiple amount of drug given the same day FCF86329BB40C F4E6EE1910940.May be 205 patients row like that
# There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day. We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day. Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data. Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.
# For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.
# Three administrations of the same drug were listed on a Friday. The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend. 
# Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate, drugname, units, surgerydate, days_at_first_drug, days_at_surg) %>%
  summarise_at(vars(amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
  separate(col= amount, paste("amount_", 1:10, sep=""), sep = ";", extra = "warn",
           fill = "right") %>%
  ungroup() %>% 
  mutate(across(starts_with("amount"), ~ na_if(., "NA"))) %>% 
  purrr::keep(~!all(is.na(.))) %>%
  mutate(across(starts_with("amount"), ~ as.numeric(.))) %>% 
  # mutate(amount_1 = as.numeric(amount_1), amount_2 = as.numeric(amount_2),
  #        amount_3 = as.numeric(amount_3), amount_4 = as.numeric(amount_4)) %>%
  mutate(amount = rowSums(select(.,amount_1:amount_4), na.rm = TRUE)) %>%
  # Found ug, ml, Ea, and NA they are all good, but 
  # ug need conversion
  # the AUC are mostly correct (real mg) but are actual AUC when < at 10 
  mutate(amount =  case_when(
    units == "ug"               ~ amount / 10, # I checked all of them
    units == "AUC" &
      amount < 10               ~ NA_real_,
    TRUE                        ~ amount
  )) %>%

@@

@@

  # Calculate expected dose
  mutate(expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
    str_detect(drugname, "taxel|platin")      ~ BSA * target_auc 
    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  )) %>% 
  mutate(expected_dose = case_when(
    expected_dose > 900 &
      target_auc == 6              ~ 900,
    expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ expected_dose
  )) %>% 
  mutate(adjusted_expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25),
    str_detect(drugname, "taxel|platin")      ~ BSA * target_auc 
    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  )) %>% 
  mutate(adjusted_expected_dose = case_when(
    adjusted_expected_dose > 900 &
      target_auc == 6              ~ 900,
    adjusted_expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ adjusted_expected_dose
  )) %>% 
  group_by(patientid) %>%
  mutate(first_treatment_date = case_when(
    str_detect(therapy, "Chemo")                      ~ min(episodedate),
    str_detect(therapy, "Surgery")                    ~ surgerydate,
  )) %>% 
  ungroup() %>% 
  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
                   duration(n=1, units = "months")) %>% 
  arrange(patientid, episodedate)
```

@@

  # Average RDI by drug by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname) %>%
  # mutate(mean_RDI_per_drug = case_when(
  #   chemotherapy_type == "Adjuvant" &
  #     linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
  #   chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  # )) %>% 
  mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  ) %>% 
  ungroup() %>% 
  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE) %>% 
  mutate(RDI_grp = case_when(
    mean_RDI_per_drug >= 0.85              ~ "correct",
    mean_RDI_per_drug < 0.85               ~ "underdose"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           levels = c("correct", "underdose"))) %>% 
  mutate(RDI_grp1 = case_when(
    mean_RDI_per_drug < 0.75               ~ "highly underdose",
    mean_RDI_per_drug >= 0.75 &
      mean_RDI_per_drug < 0.85             ~ "underdose",
    mean_RDI_per_drug >= 0.85 &
      mean_RDI_per_drug <= 1                ~ "correct",
    # mean_RDI_per_drug == 1                 ~ "perfect",
    # mean_RDI_per_drug > 1 &
    #   mean_RDI_per_drug < 1.5              ~ "higher dose",
    mean_RDI_per_drug > 1               ~ "overdose"
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          levels = c("correct", #"perfect", #"higher dose", 
                                     "overdose", 
                                     "highly underdose", "underdose")))
```
<br>
<br>

@@

# Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
#   ggplot(aes(x= chemo))+
#   geom_bar()+
#   theme_minimal(base_size = 14)+
#   coord_flip()
```
</div>
</div>

@@

Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug))+
  geom_boxplot()+
  # ylim(c(-.25, 3.5))+
  geom_jitter(shape=16)+
  labs(x = "", title = "Warning 1 dot = RDI for 1 patient") +
  theme_minimal(base_size = 14)+
  facet_wrap(.~ drugname, ncol = 2)
```
</div>

@@

Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug))+
  # geom_boxplot()+
  ylim(c(-.25, 2))+
  geom_jitter(shape=16, aes(color=RDI_grp))+
  labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
  theme_minimal(base_size = 14) +
  guides(color=FALSE)+
  facet_wrap(.~ drugname, ncol = 2)

@@

Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
  ggplot(aes(x= drugname, fill = RDI_grp))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  facet_wrap(.~ chemotherapy_type)+
  coord_flip()
```

### By Population
```{r, fig.width=12, fig.height=20}
Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
  # filter(linenumber_new == "1") %>%
  ggplot(aes(x= raceeth, y= mean_RDI_per_drug#, alpha = mean_RDI_per_drug<0.85
             ))+
  geom_boxplot(aes(fill = drugname))+
  ylim(c(0, 2))+
  scale_colour_discrete()+
  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug<0.85))+
  theme_minimal(base_size = 14)+
  facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")
```

@@

  facet_wrap(therapy ~ drugname, ncol = 3, scales = "free_x")
```

## 1.RDI summary table

<span style="color:green">**Platin**</span>  
```{r Table summary Platin}
# Treatment & demo
tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl3 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

@@

tbl_stack(list(tbl3, tbl1, tbl2),
          group_header = c("carboplatin/Neoadjuvant", 
                           "carboplatin/Adjuvant Upfront Surgery", 
                           "carboplatin/Adjuvant Upfront Chemo"),
          quiet = TRUE)
```

<span style="color:green">**Taxanes**</span>  
```{r Table summary Taxanes}
tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl3 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl4 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()
tbl5 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()
tbl6 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(type = list(mean_RDI_per_drug ~ 'continuous'),
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

@@

tbl_stack(list(tbl3, tbl1, tbl2, tbl6, tbl4, tbl5),
          group_header = c("paclitaxel/Neoadjuvant", 
                           "paclitaxel/Adjuvant Upfront Surgery", 
                           "paclitaxel/Adjuvant Upfront Chemo",
                           "PBB/Neoadjuvant", 
                           "PBB/Adjuvant Upfront Surgery", 
                           "PBB/Adjuvant Upfront Chemo"),
          quiet = TRUE)
```
<br>

<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>  
Platin  
```{r Table4 summary Platin}
# Treatment & demo
tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl3 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl4 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl5 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

@@

tbl_stack(list(tbl5, tbl3, tbl4),
          group_header = c("carboplatin/Neoadjuvant", 
                           "carboplatin/Adjuvant Upfront Surgery", 
                           "carboplatin/Adjuvant Upfront Chemo"),
          quiet = TRUE)
```
<br>

Taxanes
```{r Table4 summary Taxanes}
tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl3 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

>>>>

  # 3. Combined Multiple Administrations----
  # combined multiple amount of drug given the same day FCF86329BB40C F4E6EE1910940.May be 205 patients row like that
# There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day. We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day. Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data. Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.
# For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.
# Three administrations of the same drug were listed on a Friday. The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend. 
# Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate, drugname, units, surgerydate, days_at_first_drug, days_at_surg, diagnosisdate) %>%
  summarise_at(vars(amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
  separate(col= amount, paste("amount_", 1:10, sep=""), sep = ";", extra = "warn",
           fill = "right") %>%
  ungroup() %>% 
  mutate(across(starts_with("amount"), ~ na_if(., "NA"))) %>% 
  purrr::keep(~!all(is.na(.))) %>%
  mutate(across(starts_with("amount"), ~ as.numeric(.))) %>% 
  # mutate(amount_1 = as.numeric(amount_1), amount_2 = as.numeric(amount_2),
  #        amount_3 = as.numeric(amount_3), amount_4 = as.numeric(amount_4)) %>%
  mutate(amount = rowSums(select(.,amount_1:amount_4), na.rm = TRUE)) %>%
  # Found ug, ml, Ea, and NA they are all good, but 
  # ug need conversion
  # the AUC are mostly correct (real mg) but are actual AUC when < at 10 
  mutate(amount =  case_when(
    units == "ug"               ~ amount / 10, # I checked all of them
    units == "AUC" &
      amount < 10               ~ NA_real_,
    TRUE                        ~ amount
  )) %>%

@@

### stwp " remove patients with adj too far from sutgery
```{r}
remove_delayed_drug <- therapy_line %>% 
  mutate(interval = case_when(
    chemotherapy_type == "Adjuvant" & 
      linenumber_adj == 1       ~interval(start = surgerydate, end = linestartdate_new) / duration(n= 1, units = "months")),
  ) %>% select(patientid, episodedate, surgerydate, diagnosisdate, linenumber_new, linenumber_adj, interval, therapy, chemotherapy_type) %>% arrange(patientid, episodedate) %>% 
  filter(interval > 3) %>% 
  distinct(patientid, .keep_all = TRUE)
remove_delayed_drug <- paste(remove_delayed_drug$patientid, collapse = "|")

therapy_line <- therapy_line %>% 
  # Remove patients with more than 1 line as Neo
  filter(!str_detect(patientid, remove_delayed_drug))
therapy_line %>% distinct(patientid) %>% nrow()

@@

  # Calculate expected dose
  mutate(expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
    drugname == "paclitaxel"                  ~ BSA * target_auc 
    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  )) %>% 
  mutate(expected_dose = case_when(
    expected_dose > 900 &
      target_auc == 6              ~ 900,
    expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ expected_dose
  )) %>% 
  mutate(adjusted_expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25),
    drugname == "paclitaxel"                  ~ BSA * target_auc 
    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  )) %>% 
  mutate(adjusted_expected_dose = case_when(
    adjusted_expected_dose > 900 &
      target_auc == 6              ~ 900,
    adjusted_expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ adjusted_expected_dose
  )) %>% 
  group_by(patientid) %>%
  mutate(first_treatment_date = case_when(
    str_detect(therapy, "Chemo")                      ~ min(episodedate),
    str_detect(therapy, "Surgery")                    ~ surgerydate,
  )) %>% 
  ungroup() %>% 
  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
                   duration(n=1, units = "months")) %>% 
  arrange(patientid, episodedate)
```

@@

  # Average RDI by drug by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname) %>%
  # mutate(mean_RDI_per_drug = case_when(
  #   chemotherapy_type == "Adjuvant" &
  #     linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
  #   chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  # )) %>% 
  mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  ) %>% 
  ungroup() %>% 
  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE) %>% 
  mutate(RDI_grp = case_when(
    mean_RDI_per_drug >= 0.85              ~ "Adequate dosing",
    mean_RDI_per_drug < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           levels = c("Adequate dosing", "Underdosed"))) %>% 
  mutate(RDI_grp1 = case_when(
    mean_RDI_per_drug < 0.75               ~ "Highly underdosed",
    mean_RDI_per_drug >= 0.75 &
      mean_RDI_per_drug < 0.85             ~ "Underdosed",
    mean_RDI_per_drug >= 0.85 &
      mean_RDI_per_drug < 1.15             ~ "Adequate dosing",
    mean_RDI_per_drug >= 1.15              ~ "Overdosing"
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          levels = c("Adequate dosing",
                                     "Underdosed", 
                                     "Highly underdosed",
                                     "Overdosing")))
```
<br>
<br>

@@

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>%
  ggplot(aes(x= raceeth, fill= therapy))+
  geom_bar(position ="fill")+
  theme_minimal(base_size = 14)+
  coord_flip()+
  facet_wrap(. ~ drugname)
```
</div>
</div>

@@

Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
  ggplot(aes(x= therapy, y= mean_RDI_per_drug))+
  geom_boxplot()+
  # ylim(c(-.25, 3.5))+
  geom_jitter(shape=16)+
  labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
  theme_minimal(base_size = 14)+
  facet_wrap(.~ drugname, ncol = 2)
```
</div>

@@

Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
  ggplot(aes(x= therapy, y= mean_RDI_per_drug))+
  # geom_boxplot()+
  ylim(c(-.25, 2))+
  geom_jitter(shape=16, aes(color=RDI_grp))+
  labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
  theme_minimal(base_size = 14) +
  guides(color=FALSE)+
  facet_wrap(.~ drugname, ncol = 2)

@@

Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
  ggplot(aes(x= drugname, fill = RDI_grp))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  facet_wrap(.~ therapy)+
  coord_flip()
```

### By Population
```{r, fig.width=12, fig.height=20}
Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
  # filter(linenumber_new == "1") %>%
  ggplot(aes(x= raceeth, y= mean_RDI_per_drug#, alpha = mean_RDI_per_drug<0.85
             ))+
  geom_boxplot(aes(fill = drugname))+
  ylim(c(0, 2))+
  scale_colour_discrete()+
  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug<0.85))+
  theme_minimal(base_size = 14)+
  facet_wrap(drugname ~ therapy, ncol = 2, scales = "free")
```

@@

  facet_wrap(therapy ~ drugname, ncol = 2, scales = "free_x")
```

## 1.RDI summary table
Do you want them together in 1 table?

<span style="color:green">**Platin**</span>  
```{r Table summary Platin}
# Treatment & demo
tbl1 <- Frontline %>% filter(drugname == "carboplatin" & 
                               # chemotherapy_type == "Adjuvant" & 
                               therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl2 <- Frontline %>% filter(drugname == "carboplatin" & 
                               # chemotherapy_type == "Adjuvant" & 
                               therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

# tbl3 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
#   tbl_summary(
#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
#   bold_labels()

@@

tbl_stack(list(tbl1, tbl2),
          group_header = c(
                           "carboplatin/Upfront Surgery", 
                           "carboplatin/Upfront Chemo"),
          quiet = TRUE)
```

<span style="color:green">**Taxanes**</span>  
```{r Table summary Taxanes}
tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & 
                               # chemotherapy_type == "Adjuvant" & 
                               therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & 
                               # chemotherapy_type == "Adjuvant" & 
                               therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c("mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels()

# tbl3 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
#   tbl_summary(
#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
#   bold_labels()

# tbl4 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
#   tbl_summary(
#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
#   bold_labels()
# tbl5 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
#   tbl_summary(
#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
#   bold_labels()
# tbl6 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
#   tbl_summary(type = list(mean_RDI_per_drug ~ 'continuous'),
#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
#   bold_labels()

@@

tbl_stack(list(tbl1, tbl2),
          group_header = c(
                           "paclitaxel/Upfront Surgery", 
                           "paclitaxel/Upfront Chemo"),
          quiet = TRUE)
```
<br>

<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>  
Removing the overall on the right side? Or do you want the tables separated?
Platin  
```{r Table4 summary Platin}
# Treatment & demo
tbl1 <- Frontline %>% filter(drugname == "carboplatin" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl3 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "carboplatin" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl4 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

# tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
#   tbl_summary(by = raceeth,
#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
#   tbl_summary(by = bmi_cat,
#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl5 <-
#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

@@

tbl_stack(list(tbl3, tbl4),
          group_header = c(
                           "carboplatin/Upfront Surgery", 
                           "carboplatin/Upfront Chemo"),
          quiet = TRUE)
```
<br>

Taxanes
```{r Table4 summary Taxanes}
tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl3 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
